---
title: "CENG 4515 Data Science and Analytics Project"
author: "Ozan Kahramanoğlu"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
Sys.setenv(PATH = paste(Sys.getenv("PATH"), "C:\\Users\\ozank\\AppData\\Local\\Programs\\MiKTeX 2.9\\miktex\\bin\\x64", sep=.Platform$path.sep))
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
<h2>Introduction<h2>

<h2>HYPOTHESIS<h2>
<p>
The dataset, provided by Peerindex, comprises a standard, 
pair-wise preference learning task. Each datapoint describes 
two individuals. Pre-computed, standardised features based on
twitter activity (such as volume of interactions,
number of followers, etc) is provided for each individual.

This project help us to understand which parameters are important
to be a influencer in Twitter
</p>

<p>
This is the report of CENG 4515 Data Science and Analytics project
</p>

<p>
This is the report consist of 4 main part
<ul>Introduction</ul>
<ul>Body</ul>
<ul>Conclusion</ul>
<ul>Appendix</ul>

<h2>Body<h2>

</p>
<h2>WORKING DIRECTORY<h2>
<p>
First we should set our working directory 
Change this directory according to your computer and OS
</p>
```{r}
#setwd("C:/Users/ozank/Desktop/DataScienceProject/")
```


```{r}
# if you dont have necessary packages you should run next block of code (A.K.A dependencies) 

#install.packages("caret" , dependencies = TRUE)
#install.packages("dplyr", dependencies = TRUE)
#install.packages("ggplot2", dependencies = TRUE)
#install.packages("skimr", dependencies = TRUE)
#install.packages("kernlab", dependencies = TRUE)
#install.packages("corrplot", dependencies = TRUE)
```

<h2>NECESSARY LIBRARIES<h2>

Then we should include our necessary packages



```{r}
library(caret)
library(dplyr)
library(ggplot2)
library(skimr)
library(kernlab)
library(corrplot)
```
  
<h2>IMPORTING DATA<h2>  

<p>Data is seperated by the provider to three different CSV's</p>
```{r}
data <- read.csv("train.csv")
testdata <- read.csv("test.csv")
sample_data <- read.csv("sample_predictions.csv")
```

<p>
This data used for competitons so "sample_predictions.csv"
file some kind of a test file we should do some modifications
to our test data and train data have to same number of colums
The index number is the same for sample data and test data
So all we need to do is adding to second column of sample data
to the end of test data
</p>


```{r}

testdata$Choice <- sample_data[,2]

# Now we dont need sample data.

object.size(testdata) # Reports the memory size allocated to the object
# Test data allocate 908680 bytes
object.size(data) # Reports the memory size allocated to the object
# Data allocate 817344 bytes
object.size(sample_data) # Reports the memory size allocated to the object
# Sample data allocate 72200 bytes

# So we can free 72200 bytes from our memeory

rm(sample_data)

```
  

<p>
Now we dont need sample data.
So we can free 72200 bytes from our memeory
</p>

<h2>DATA EXPLORING</h2>

```{r}
head(data)
```

<p>
We can see that Choice column has binary output
All the other columns has numerical output
</p>

<p>
If there is some NA's needs to be handled below
code block will be handle it but there isn't any
NA in the data.
</p>

```{r}
if (anyNA(data)) {
  anyNA(data)
  print(" There some NA's need to be omitted ")
  data <- na.omit(data)
} else{
  print("No NA's found to be omitted")
}
```


<p>
We can take look to feature graph
</p>

```{r}
featurePlot(x = data[,2:23], 
            y = as.factor(data$Choice), 
            plot = "density",
            strip=strip.custom(par.strip.text=list(cex=.5)),
            scales = list(x = list(relation="free"), 
                          y = list(relation="free")))
```

<p>
It is hard to say anything about the data with this 
feature plot because there is no distict graph 
</p>

<p>
We can skim the data for more information about dataset
</p>

```{r}
skim(data)
```

<p>
Also we can take look to correlation plot
</p>

```{r}
corrplot(
  cor(data),
  method = "color",
  outline = T,
  order = "hclust",
  cl.pos = "b",
  tl.col = "indianred4",
  tl.cex = 0.5,
  cl.cex = 0.5,
  addCoef.col = "white",
  number.digits = 2,
  number.cex = 0.3,
  col = colorRampPalette(c("darkred", "white", "midnightblue"))(100)
)

```

<h2>LOGISTIC REGRESSION</h2>

<p>
In another case data should be splited to two parts
as training and testing part but data provider already
splited and we do the necerrasy tweaks in the data import
part
</p>

<p>
According to binomial output we should you generalized linear
model to generating a binomial model
</p>

```{r}
data.glm <- glm(data$Choice ~. ,family = binomial(), data = data)
summary(data.glm)
```

<p>
We can see here our residuals are acceptable
</p>

<p>
We can take a better look to ther residuals in this plot
</p>

```{r}
a <- plot(
  predict(data.glm),
  residuals(data.glm),
  col = c("blue", "red"),
  lines(lowess(predict(data.glm), residuals(data.glm)), col = "red"))
  abline(h = 0, lty = 2, col = "grey")

```

<h2>MACHINE LEARNING MODELS</h2>

<p>
The data should be divided into two part with this block of code
but our data already divided and necessary tweaks already handled
in the data import part
Otherwise this code will be uncommented
</p>

```{r}
# set.seed(100)
# trainRowNumbers <- createDataPartition(data$Choice, p=0.7, list=FALSE)
# 
# data <- data[trainRowNumbers,]
# testdata <- data[-trainRowNumbers,]
```

<p>
Now we will create a control method to use in traning our models
</p>


```{r}
fitControl <- trainControl(
  method = 'repeatedcv',                   # k-fold cross validation
  number = 10,                      # number of folds
  repeats = 2
) 
```

<h2>KNN model</h2>
<p>
Now we will train KNN model
</p>

```{r}
KNN_train <-
  train(
    y = as.factor(data$Choice),
    x = data[, 2:23] ,
    preProcess = c("center", "scale"),
    trControl = fitControl ,
    method = "knn"
  )
```

<p>
We can take look at variable importance with this graph
</p>

```{r}
varimp_KNN <- varImp(KNN_train)
plot(varimp_KNN, main="Variable Importance with varimp_KNN")
```

<p>
Now we can test our KNN model and see the results 
</p>

```{r}
testDataKNN <- predict(KNN_train, testdata)  
confKNN <- confusionMatrix(reference = as.factor(ifelse(testdata$Choice> 0.5,1,0)), data = testDataKNN, mode='everything', positive='1')
confKNN
fourfoldplot(confKNN$table)
```

<p>
In adittion to this we can take look to density
plot of accuracy of this model
</p>

```{r}
densityplot(KNN_train$results$Accuracy)
```

<h2>Random Forest (RF) model</h2>

<p>
Now we will train Random Forest (RF) model
</p>

```{r}
RF_train <-
  train(
    y = as.factor(data$Choice),
    x = data[, 2:23] ,
    preProcess = c("center", "scale"),
    trControl = fitControl ,
    method = "rf"
  )
```

<p>
We can take look at variable importance with this graph
</p>

```{r}
varimp_RF <- varImp(RF_train)
plot(varimp_RF, main="Variable Importance with RF_train")
```

<p>
Now we can test our RF model and see the results 
</p>

```{r}
testDataRF <- predict(RF_train, testdata)  
confRF <- confusionMatrix(reference = as.factor(ifelse(testdata$Choice> 0.5,1,0)), data = testDataRF, mode='everything', positive='1')
confKNN
fourfoldplot(confRF$table)
```

<p>
In adittion to this we can take look to density
plot of accuracy of this model
</p>

```{r}
densityplot(RF_train$results$Accuracy)
```

<h2>Radial Support Vector Machine (svmRadial) model</h2>

<p>
Now we will train Radial Support Vector Machine (svmRadial) model
</p>

```{r}
sigDist <- sigest(data$Choice ~ ., data = data, frac = 1)
svmTuneGrid <- data.frame(.sigma = sigDist[1])

SVM_train <-
  train(
    y = as.factor(data[,1]),   
    x = data[, 2:23],
    preProcess = c("center", "scale"),
    method = "svmRadial" ,
    trControl = fitControl 
  )
```

<p>
We can take look at variable importance with this graph
</p>

```{r}
varimp_SVM <- varImp(SVM_train)
plot(varimp_SVM, main="Variable Importance with SVM_train")
```

<p>
Now we can test our SVM model and see the results 
</p>

```{r}
testDataSVM <- predict(SVM_train)  
confSVM <- confusionMatrix(reference = unlist(as.factor(ifelse(testdata$Choice>= 0.5,'1','0')))[1:5500] , data = testDataSVM, mode='everything', positive='1', dnn = c("Prediction", "Reference"))
confSVM
fourfoldplot(confSVM$table)
```

<p>
In adittion to this we can take look to density
plot of accuracy of this model
</p>

```{r}
densityplot(SVM_train$results$Accuracy)
```

<h2>Conclusion<h2>

<p>
Lets look at the boxplot of models' accuracy 
</p>

```{r}
par(mfrow=c(1,3)) 
graphics::boxplot(SVM_train$results$Accuracy)
graphics::boxplot(RF_train$results$Accuracy)
graphics::boxplot(KNN_train$results$Accuracy)

```

<p>
With a little diffrence the best model is Random Forest
</p>

<p>
In conclusion in this project we can see what to do to be 
a influencer in twitter.
We can take a look to  variable importance plots to how to 
be a better influencer
Also we can use the random forest model to predict can a 
Twitter account will be a influencer account
</p>


<h1>Appendix<h1>

<h2>DATA SOURCE<h2>
<p>
Every piece of data that are used in this project can be found on the link which is below

Data url https://www.kaggle.com/c/predict-who-is-more-influential-in-a-social-network/data
</p>



